### 2023-09-04 proofs/tex/decl-typing-lemmas.tex
WIP: separate the algorithmic proofs
Grammar update: Γ = set

            By inversion of $[[Γ ; Φ ⊢ ∀pas1.iN1' ● args ⇒> iM]]$:
            \begin{enumerate}
                \item $[[Γ ⊢ σ : pas1]]$        
                \item $[[Γ ; Φ ⊢ [σ]iN1' ● args ⇒> iM]]$
                \item $[[args ≠ ·]]$
            \end{enumerate}

            Let us construct $[[Γ ⊢ σ0 : pas2]]$ in the following way:
            $$
            \begin{cases}
                [[ [σ0]α⁺ =  [σ][mu]α⁺ ]] & \text{if } [[α⁺]] \in [[ {pas2} ∩ fv iN2' ]] \\
                [[ [σ0]α⁺ =  ∃β⁻.↓β⁻ ]] & \text{otherwise (the type does not matter here)} \\
            \end{cases}
            $$

            Then to infer $[[Γ ; Φ ⊢ iN2 ● args ⇒> iM]]$, we 
            apply \ruleref{\ottdruleDTArrowAppLabel} with $[[σ0]]$. 
            Let us show the required premises:
            \begin{enumerate}
                \item $[[Γ ⊢ σ0 : pas2]]$ by construction;
                \item $[[args ≠ ·]]$ as noted above;
                \item To show $[[Γ ; Φ ⊢ [σ0]iN2' ● args ⇒> iM]]$,
                Notice that $[[ [σ0]iN2' = [σ][mu]iN2' ]]$   
                and since $[[ [mu]iN2' ≈ iN1' ]]$, $[[ [σ][mu]iN2' ≈ [σ]iN1' ]]$.
                This way, by \cref{lemma:equiv-soundness}, $[[Γ ⊢ [σ]iN1' ≈ [σ0]iN2']]$.
                Then the required judgement holds by the induction hypothesis
                applied to $[[Γ ; Φ ⊢ [σ]iN1' ● args ⇒> iM]]$.
            \end{enumerate}
    \end{caseof}
\end{proof}

\newcommand{\pureSize}[1]{\ensuremath{\mathsf{pure\_size}(#1)}}
\newcommand{\metric}[1]{\ensuremath{\mathsf{metric}(#1)}}
\newcommand{\eqNodes}[1]{\ensuremath{\mathsf{eq\_nodes}(#1)}}
\newcommand{\size}[1]{\ensuremath{\mathsf{size}(#1)}}
\newcommand{\npq}[1]{\ensuremath{\mathsf{npq}(#1)}}

@@

            By inversion, we have $[[σ]]$ such that $[[Γ ⊢ σ : pas]]$ and
            $[[Γ ; Φ1 ⊢ [σ]iN ● args ⇒> iM]]$ is inferred.
            Let us denote the inference tree as $T_1'$.
            Notice that the induction hypothesis is applicable to $T_1'$:
            $\metric{T_1'} = ((\size{[[args]]}, 0), x)$ is less than 
            $\metric{T_1} = ((\size{[[args]]}, |[[pas]]|), y)$ for any $x$ and $y$,
            since $|[[pas]]| > 0$ by inversion.

            This way, by the induction hypothesis, 
            there exists a tree $T_2'$ inferring
            $[[Γ ; Φ2 ⊢ [σ]iN ● args ⇒> iM]]$.
            Notice that the premises $[[args ≠ ·]]$, $[[Γ ⊢ σ : pas]]$,
            and $[[pas ≠ ·]]$ do not depend on the variable context,
            and hold by inversion.
            Then we infer $[[Γ ; Φ2 ⊢ ∀pas.iN ● args ⇒> iM]]$ by \ruleref{\ottdruleDTForallAppLabel}.
    \end{caseof}
\end{proof}

>>>>

            By inversion of $[[Γ ; Φ ⊢ ∀pas1.iN1' ● args ⇒> iM]]$:
            \begin{enumerate}
                \item $[[Γ ⊢ σ :{pas1}]]$        
                \item $[[Γ ; Φ ⊢ [σ]iN1' ● args ⇒> iM]]$
                \item $[[args ≠ ·]]$
            \end{enumerate}

            Let us construct $[[Γ ⊢ σ0 :{pas2}]]$ in the following way:
            $$
            \begin{cases}
                [[ [σ0]α⁺ =  [σ][mu]α⁺ ]] & \text{if } [[α⁺]] \in [[ {pas2} ∩ fv iN2' ]] \\
                [[ [σ0]α⁺ =  ∃β⁻.↓β⁻ ]] & \text{otherwise (the type does not matter here)} \\
            \end{cases}
            $$

            Then to infer $[[Γ ; Φ ⊢ iN2 ● args ⇒> iM]]$, we 
            apply \ruleref{\ottdruleDTArrowAppLabel} with $[[σ0]]$. 
            Let us show the required premises:
            \begin{enumerate}
                \item $[[Γ ⊢ σ0 :{pas2}]]$ by construction;
                \item $[[args ≠ ·]]$ as noted above;
                \item To show $[[Γ ; Φ ⊢ [σ0]iN2' ● args ⇒> iM]]$,
                Notice that $[[ [σ0]iN2' = [σ][mu]iN2' ]]$   
                and since $[[ [mu]iN2' ≈ iN1' ]]$, $[[ [σ][mu]iN2' ≈ [σ]iN1' ]]$.
                This way, by \cref{lemma:equiv-soundness}, $[[Γ ⊢ [σ]iN1' ≈ [σ0]iN2']]$.
                Then the required judgement holds by the induction hypothesis
                applied to $[[Γ ; Φ ⊢ [σ]iN1' ● args ⇒> iM]]$.
            \end{enumerate}
    \end{caseof}
\end{proof}

\newcommand{\pureSize}[1]{\ensuremath{\mathsf{pure\_size}(#1)}}
\newcommand{\metric}[1]{\ensuremath{\mathsf{metric}(#1)}}
\newcommand{\eqNodes}[1]{\ensuremath{\mathsf{eq\_nodes}(#1)}}
\newcommand{\npq}[1]{\ensuremath{\mathsf{npq}(#1)}}

@@

            By inversion, we have $[[σ]]$ such that $[[Γ ⊢ σ :{pas}]]$ and
            $[[Γ ; Φ1 ⊢ [σ]iN ● args ⇒> iM]]$ is inferred.
            Let us denote the inference tree as $T_1'$.
            Notice that the induction hypothesis is applicable to $T_1'$:
            $\metric{T_1'} = ((\size{[[args]]}, 0), x)$ is less than 
            $\metric{T_1} = ((\size{[[args]]}, |[[pas]]|), y)$ for any $x$ and $y$,
            since $|[[pas]]| > 0$ by inversion.

            This way, by the induction hypothesis, 
            there exists a tree $T_2'$ inferring
            $[[Γ ; Φ2 ⊢ [σ]iN ● args ⇒> iM]]$.
            Notice that the premises $[[args ≠ ·]]$, $[[Γ ⊢ σ :{pas}]]$,
            and $[[pas ≠ ·]]$ do not depend on the variable context,
            and hold by inversion.
            Then we infer $[[Γ ; Φ2 ⊢ ∀pas.iN ● args ⇒> iM]]$ by \ruleref{\ottdruleDTForallAppLabel}.
    \end{caseof}
\end{proof}
